---
title: "Schedule"
slug: schedule
summary: "Schedule of the Gov 2002 semester with readings, due dates, and links to materials."
toc: false
sidebar: false
page-layout: full
---


```{r packages-data, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(lubridate)
library(glue)

schedule <- read_csv("data/schedule.csv", show_col_types = FALSE) 
```

Below is the schedule for the semester with the reading, tutorials, and problem sets/exams due in each week of course. You can find the lecture videos under the “Materials” links for that week. You should generally:

- watch the lecture videos and complete the readings by Monday;
- complete the tutorials by Monday evening at 11:59pm; and
- submit the problem set or exam by Wednesday at 11:59pm.

Here's a guide to the schedule:

- [**Materials**](/materials/) ({{< fa book-open-reader >}}): This page contains the readings, slides, and recorded lectures for the topic. Read and watch these first.
- **Assignment** ({{< fa pen-ruler >}}): This page contains the instructions for each assignment. **Assignments are due by 11:59 PM on the day they're listed.**




```{r build-table, echo=FALSE, results="asis"}
schedule <- schedule %>%
    mutate(var_title = ifelse(!is.na(content),
                              glue('<span class="content-title">{title}</span>'),
                              glue('{title}'))) %>%
    mutate(var_deadline = ifelse(!is.na(deadline),
                                 glue('&emsp;&emsp;<small>(submit by {deadline})</small>'),
                                 glue(""))) %>%
    mutate(var_content = ifelse(!is.na(content),
                                glue('<a href="{content}.qmd"><i class="fa-solid fa-book-open-reader fa-lg"></i></a>'),
                                glue('<font color="#e9ecef"><i class="fa-solid fa-book-open-reader fa-lg"></i></font>'))) %>%
    mutate(var_example = ifelse(!is.na(example),
                                glue('<a href="{example}.qmd"><i class="fa-solid fa-laptop-code fa-lg"></i></a>'),
                                glue('<font color="#e9ecef"><i class="fa-solid fa-laptop-code fa-lg"></i></font>'))) %>%
    mutate(var_assignment = ifelse(!is.na(assignment),
                                   glue('<a href="{assignment}.qmd"><i class="fa-solid fa-pen-ruler fa-lg"></i></a>'),
                                   glue('<font color="#e9ecef"><i class="fa-solid fa-pen-ruler fa-lg"></i></font>'))) %>%
    mutate(col_date = ifelse(is.na(date_end),
                             glue('<strong>{format(date, "%B %e")}</strong>'),
                             glue('<strong>{format(date, "%B %e")}</strong>–<strong>{format(date_end, "%B %e")}</strong>'))) %>%
    mutate(col_title = glue('{var_title}{var_deadline}')) %>%
    mutate(col_content = var_content,
           col_example = var_example,
           col_assignment = var_assignment) %>%
  select(Week = week, Date = col_date, Title = col_title, Content = col_content,
         Example = col_example, Assignment = col_assignment)

week_count <- schedule |> count(Week)
week_index <- week_count |> pull(n) |> set_names(paste0("Week ", week_count$Week))
 
tbl <- schedule |>
  select(-Week) |>
  kbl(escap = FALSE, align = "rllccccc", table.attr = 'class="schedule-table"') |>
  kable_styling() |>
  column_spec(1, width = "20%", extra_css = "padding-right: 20px;") %>% 
  column_spec(2, width = "50%") %>% 
  column_spec(c(3:5), width = "10%") |>
  pack_rows(index = week_index,
              label_row_css = "border-bottom: 2px solid #000000;")

  cat(tbl)
```

 
