---
title: "Summarizing Relationships, Tidying and Joining Data"
date: 2022-10-04
---


## Readings 

- For summarizing relationships, see QSS 3.6 and MD 5.1.1. 
- For pivoting and tidy data, see MD Ch 4. 
- For more on joins, see the [chapter 20](https://r4ds.hadley.nz/joins.html) in R for Data Science.

## Data

- Reinstall the Gov 50 data package that has new data for this week:
```{r}
#| eval: false
remotes::install_github("mattblackwell/gov50data")
```

- If you cannot install the package, you can download the data locally at [`covid_votes.csv`](/files/data/covid_votes.csv)  to the same directory as your Rmd file and load it using:
```{r}
#| eval: false
library(tidyverse)
covid_votes <- read_csv("covid_votes.csv")
```

- For Thursday lecture, we added to additional data sets to `gov50data`. If you cannot install that package, then you can download them: [`mortality.csv`](/files/data/mortality.csv) and [`spotify.csv`](/files/data/spotify.csv). Put them in the same folder as your Rmd file and use these commands to load:
```{r}
#| eval: false
library(tidyverse)
mortality <- read_csv("mortality.csv")
spotify <- read_csv("spotify.csv")
```

- We will also use data from the `nycflights13` package that you can install with:
```{r}
#| eval: false
install.packages("nycflights13")
```




## Slides and Code

- Tuesday (10/4) lecture: Summarizing relationships and writing our own functions
  - [PDF of slides as I present them](/slides/10_bivariate.pdf)
  - [PDF of handout version of slides](/slides/10_bivariate_handout.pdf) (no incremental slides)
  - Code: [`covid_votes.Rmd`](/files/code/covid_votes.Rmd)

- Thursday (10/6) lecture: Causality review, pivoting longer, joining data.
  - [PDF of slides as I present them](/slides/11_tidy_joins.pdf)
  - [PDF of handout version of slides](/slides/11_tidy_joins_handout.pdf) (no incremental slides)
   - Code: [`lecture-11.Rmd`](/files/code/lecture-11.Rmd)

